LSOA domestic Electricty and Gas maps

### 2021-09-02 LSOA domestic Elec and Gas.Rmd
added IMD score checks

lsoa_sf_de20102019$pc_diff <- 100*(lsoa_sf_de20102019$de_diff/lsoa_sf_de20102019$de2010)
t_diff <-  dplyr::select(as.data.frame(lsoa_sf_de20102019), 
                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Name.y`,
                         de2010, de2019, de_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x = pc_diff)) +
  geom_histogram()
```
####Plotting the change in dom elec consumption against the deprevation score
```{r Loading in the Deprevation score data}
inFile<-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
LSOAdep<-readr::read_csv(inFile)
LSOAdep$'LSOA11CD' <- LSOAdep$'lsoa11cd'
head(LSOAdep)
names(LSOAdep)
```
```{r plotting change in elec usage against dep}
LSOAdepelec <- merge(merged_de, LSOAdep, by= "LSOA11CD")
names(LSOAdepelec)
df <- dplyr::select(LSOAdepelec, LSOA11CD, "Local Authority Name.x", "de_diff", IMDScore, de2010, IMD_Decile
)

@@

>>>>

lsoa_sf_de20102019$pc_diff <- 100*(lsoa_sf_de20102019$de_diff/lsoa_sf_de20102019$de2010)
t_diff <-  dplyr::select(as.data.frame(lsoa_sf_de20102019), 
                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Name.y`,
                         de2010, de2019, de_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x = pc_diff)) +
  geom_histogram()
```
#### Plotting the change in dom elec consumption against the deprivation score

Loading deprivation data and double checking what the IMD Decile means

```{r Loading in the Deprivation score data}
inFile<-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
LSOAdep<-readr::read_csv(inFile)
LSOAdep$'LSOA11CD' <- LSOAdep$'lsoa11cd'
head(LSOAdep)
names(LSOAdep)

# check IMD decile is higher with higher deprivation
library(data.table)
dt <- as.data.table(Solent)
dt[, .(nLSOAs = .N,
       meanIMDScore = mean(IMDScore)),
   keyby = .(IMD_Decile)]

ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y = IMDScore, 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "IMD Score")
```

NB: IMD Decile 10 has _LOWER_ IMD score!

```{r plotting change in elec usage against dep}
LSOAdepelec <- merge(merged_de, LSOAdep, by= "LSOA11CD")
names(LSOAdepelec)
df <- dplyr::select(LSOAdepelec, LSOA11CD, "Local Authority Name.x", "de_diff", IMDScore, de2010, IMD_Decile
)

@@

Try adding facets for each Local Authority
